### 2016-02-08 ch05-initvals/InitialValuesPaper.tex
Some work on init-vals

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\onecolumnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  %\input{\thisDir/fig/elvis-spectra.tikz}
  %TODO: simplify figure
  \caption[Measured input/output spectra of \BK{} filter.]{Input $U^{[r]}(\omega)$ and output $Y^{[r]}(\omega)$ spectra~\legref[2]{leg:SpectraMeasurement:U:single} measured using the Elvis.
  \legref[2]{leg:SpectraMeasurement:U:mean}: the mean spectra $\tilde{U}$ and $\tilde{Y}$, \legref[2]{leg:SpectraMeasurement:U:noise}: noise levels $\hat\sigma_U$ and $\hat\sigma_Y$.}
  \label{fig:SpectraMeasurement}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/overview-cost-val.tikz}
  \caption[$\costFunc{\bullet}$ and $\validationDistance{\bullet}$ for each repeated measurement.]{Cost function $V(\model{\bullet})$ and validation distance of the model estimated in each repetition of the measurement.
  Based on the cost function, $\model{RFIR}$~\legref{leg:RFIR} is not always the best estimate $\model{best}$~\legref{leg:best}.
  Especially in the validation plot (bottom), $\model{RFIR}$ performs (almost) as well or even better than $\model{exist}$~\legref{leg:exist} and $\model{trunc}$~\legref{leg:trunc}.
  Both latter methods often produce models that perform poorly compared to $\| G_{VXI} \|$~\legref{leg:reference} and $\model{VXI}$~\legref{leg:VXI}.
  This means that in our limited experimental study, the performance degradation of choosing RFIR to produce initial values over the studied alternatives is negligible.}
  \label{fig:overview}
\end{figure}

\begin{figure}
  \centering
  \ref{leg:init:secondBest}
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.60\figurewidth}
  \input{\thisDir/fig/special-histogram.tikz}
  \caption[Performance degradation/enhancement for selecting the second best model.]{
  Performance degradation/enhancement ($X_{\bullet}-X_{\mathrm{best}}$) for choosing a given method $\bullet$ instead of the `best' method for the measurement example in this chapter.
  In red/orange the positive values ($X_{\bullet} > X_{\mathrm{best}}$), the performance degradation for using $\model{\bullet}$ over $\model{best}$ is shown.
  The negative values ($X_{\bullet} < X_{\mathrm{best}}$), i.e. the performance enhancement (for using $\model{\bullet}$ instead of $\model{best}$) is shown in green/blue.
  Zero values (i.e. $X_{\bullet} = X_{\mathrm{best}}$) are not shown, hence the data shows when method $\bullet$ is \emph{not} selected as the `best' method.
  The dashed lines are the minimum, median and maximum of $X_{\bullet}$ to give a sense of scale.
  The performance degradation of choosing $\model{RFIR}$ instead of $\model{best}$ is smaller than the corresponding performance degradation for the other methods.
  The performance enhancement from choosing $\model{RFIR}$ over $\model{best}$, is almost on par with the corresponding performance degradation (i.e. there is little to gain \emph{or} lose from choosing $\model{RFIR}$ over $\model{best}$).
  For $\model{trunc}$ and $\model{exist}$, there is much less performance to gain from picking those over $\model{best}$ and there is a lot more to lose.
  }
  \label{fig:init:histogramEnhancement}
\end{figure}

@@

\subsection{Stress test of the smoothers}
To test the effectiveness of the initial estimates obtained from these particular smoothers, an extra set of $n_{\mathrm{MC}} = 100$ Monte Carlo simulations were performed.
In particular, all combinations of
\begin{itemize}
  \item low-pass, high-pass, band-pass and band-stop 
  \item Chebyshev Type I, Chebyshev Type II, Elliptical and Butterworth
\end{itemize}
discrete-time filters (see \figref{fig:bodeplots} and \tabref{tbl:init:stresstest}) of tenth degree generated by the MATLAB functions \texttt{cheby1}, \texttt{cheby2}, \texttt{ellip} and \texttt{butter} and an SNR of $20 \unit{dB}$ and $N=1024$ measured samples.
All filters $G$ have been normalized in such a way that $\norm[2]{G} = 1$.
The low-pass and high-pass filtes have a cross-over frequency of $\frac{\pi}{2} \unit{rad/S}$. 
The band-pass, respectively band-stop, filters have a passband, respectively stopband, in the frequency range$\left[ \frac{2\pi}{5}, \frac{3\pi}{5}\right] \unit{rad/S}$.
Note also that both the band-pass and band-stop filters have a McMillan degree of 20 as per the \MATLAB conventions.

The input excitation and the disturbing output noise were both white and Gaussian.

@@

Thus, the work in this chapter has demonstrated the effectiveness of the studied \gls{FRF} smoothing techniques in enhancing the initial values.
Consequently, the ease-of-use of parametric model fitting can be increased considerably by making it possible to obtain good parametric models without requiring any additional user interaction.

>>>>

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\onecolumnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/elvis-spectra.tikz}
  %TODO: simplify figure
  \caption[Measured input/output spectra of \BK{} filter.]{Input $U^{[r]}(\omega)$ and output $Y^{[r]}(\omega)$ spectra~\legref[2]{leg:SpectraMeasurement:U:single} measured using the Elvis.
  \legref[2]{leg:SpectraMeasurement:U:mean}: the mean spectra $\tilde{U}$ and $\tilde{Y}$, \legref[2]{leg:SpectraMeasurement:U:noise}: noise levels $\hat\sigma_U$ and $\hat\sigma_Y$.}
  \label{fig:SpectraMeasurement}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/overview-cost-val.tikz}
  \caption[$\costFunc{\bullet}$ and $\validationDistance{\bullet}$ for each repeated measurement.]{Cost function $V(\model{\bullet})$ and validation distance of the model estimated in each repetition of the measurement.
  Based on the cost function, $\model{RFIR}$~\legref{leg:RFIR} is not always the best estimate $\model{best}$~\legref{leg:best}.
  Especially in the validation plot (bottom), $\model{RFIR}$ performs (almost) as well or even better than $\model{exist}$~\legref{leg:exist} and $\model{trunc}$~\legref{leg:trunc}.
  Both latter methods often produce models that perform poorly compared to $\| G_{VXI} \|$~\legref{leg:reference} and $\model{VXI}$~\legref{leg:VXI}.
  This means that in our limited experimental study, the performance degradation of choosing RFIR to produce initial values over the studied alternatives is small.}
  \label{fig:overview}
\end{figure}

\begin{figure}
  \centering
  \ref{leg:init:secondBest}
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.60\figurewidth}
  \input{\thisDir/fig/special-histogram.tikz}
  \caption[Performance degradation/enhancement for selecting the second best model.]{
  Performance degradation/enhancement ($X_{\bullet}-X_{\mathrm{best}}$) for choosing a given method $\bullet$ instead of the `best' method for the measurement example in this chapter.
  In red/orange the positive values ($X_{\bullet} > X_{\mathrm{best}}$), the performance degradation for using $\model{\bullet}$ over $\model{best}$ is shown.
  The negative values ($X_{\bullet} < X_{\mathrm{best}}$), i.e. the performance enhancement (for using $\model{\bullet}$ instead of $\model{best}$) is shown in green/blue.
  Zero values (i.e. $X_{\bullet} = X_{\mathrm{best}}$) are not shown, hence the plot shows when method $\bullet$ is \emph{not} selected as the `best' method.
  The dashed lines are the minimum, median and maximum of $X_{\bullet}$ to give a sense of scale.
  The performance degradation of choosing $\model{RFIR}$ instead of $\model{best}$ is smaller than the corresponding performance degradation for the other methods.
  The performance enhancement from choosing $\model{RFIR}$ over $\model{best}$, is almost on par with the corresponding performance degradation (i.e. there is little to gain \emph{or} lose from choosing $\model{RFIR}$ over $\model{best}$).
  For $\model{trunc}$ and $\model{exist}$, there is much less performance to gain from picking those over $\model{best}$ and there is a lot more to lose.
  }
  \label{fig:init:histogramEnhancement}
\end{figure}

@@

\subsection{Stress test of the smoothers}
To test the effectiveness of the initial estimates obtained from these particular smoothers, an extra set of $n_{\mathrm{MC}} = 100$ Monte Carlo simulations were performed.
In particular, all combinations of
\begin{itemize}
  \item low-pass, high-pass, band-pass and band-stop 
  \item Chebyshev Type I, Chebyshev Type II, Elliptical and Butterworth
\end{itemize}
discrete-time filters (see \figref{fig:bodeplots} and \tabref{tbl:init:stresstest}) of tenth degree generated by the MATLAB functions \texttt{cheby1}, \texttt{cheby2}, \texttt{ellip} and \texttt{butter} are simulated.
Each of these filters $\true{G}$ has been normalized such that $\norm[2]{\true{G}} = 1$.
The low-pass and high-pass filtes have a cross-over frequency of $\frac{\pi}{2} \unit{rad/S}$. 
The band-pass, respectively band-stop, filters have a passband, respectively stopband, in the frequency range$\left[ \frac{2\pi}{5}, \frac{3\pi}{5}\right] \unit{rad/S}$.
Note also that both the band-pass and band-stop filters have a McMillan degree of 20 as per the \MATLAB conventions.

The input excitation and the disturbing output noise were $N=1024$ samples of white Gaussian noise such that and an SNR of $20 \unit{dB}$ was attained at the output.
Note that due to $\norm[2]{\true{G}}=1$, the validation distance $\norm{\model{G} - \true{G}}$ is exactly the relative \gls{RMS} estimation error of the transfer function.

@@

Thus, the work in this chapter has demonstrated the effectiveness of the studied \gls{FRF} smoothing techniques in enhancing the initial values.
Consequently, the quality of parametric estimates can be increased considerably by using non-parametric \gls{FRF} models to initialize the non-convex optimization problem of fitting a rational transfer function model.
Hence, the ease-of-use of parametric model fitting can be increased significantly by having high-quality non-parametric \gls{FRF} models.
This comes at a limited cost for the end-user: in principle these smoothers can be tried without any additional intervention by the user.
The only disadvantage is the additional computational effort required and hence also the increase in wall clock time to obtain a parametric estimate.
However, thanks to the recent trend of parallel computing and the fact that this problem is embarrassingly parallel, we expect that increases in wall-clock time can be kept very modest.
